Numerical simulation of the Cordilleran ice sheet through the last glacial cycle

### 2014-05-27 cordillera-cycle.tex
Use 6.1 degC offset for NGRIP.

% tab:records
\begin{table*}[t]
  \caption{Palaeo-temperature proxy records and scaling parameters used to
           prepare temperature offset time-series used to force the ice sheet
           model through the last 120\,\unit{kyr}. $T_{[32;22]}$ refers to the
           mean temperature anomaly during the period -32 to~-22~\unit{kyr} after
           scaling.}
  \label{tab:records}
  {\begin{tabular}{lcccc}
    \tophline
    Record & Proxy & Scaling factor & $T_{[32;22]}$ & Source\\
    \middlehline
    GRIP     & \chem{\delta^{18}O} & ?\% & -5.8{\degree}C & \aref \\
    NGRIP    & \chem{\delta^{18}O} & ?\% & -6.0{\degree}C & \aref \\
    EPICA    & \chem{\delta^{18}O} & ?\% & -5.6{\degree}C & \aref \\
    Vostok   & \chem{\delta^{18}O} & ?\% & -5.6{\degree}C & \aref \\
    ODP~1012 & \chem{U^{K'}_{37}}  & ?\% & -5.8{\degree}C & \aref \\
    ODP~1020 & \chem{U^{K'}_{37}}  & ?\% & -5.8{\degree}C & \aref \\
    \bottomhline
  \end{tabular}}
  \belowtable{}
\end{table*}

>>>>

% tab:records
\begin{table*}[t]
  \caption{Palaeo-temperature proxy records and scaling parameters used to
           prepare temperature offset time-series used to force the ice sheet
           model through the last 120\,\unit{kyr}. $T_{[32;22]}$ refers to the
           mean temperature anomaly during the period -32 to~-22~\unit{kyr} after
           scaling.}
  \label{tab:records}
  {\begin{tabular}{lcccc}
    \tophline
    Record & Proxy & Scaling factor & $T_{[32;22]}$ & Source\\
    \middlehline
    GRIP     & \chem{\delta^{18}O} & ?\% & -5.8{\degree}C & \aref \\
    NGRIP    & \chem{\delta^{18}O} & ?\% & -6.1{\degree}C & \aref \\
    EPICA    & \chem{\delta^{18}O} & ?\% & -5.6{\degree}C & \aref \\
    Vostok   & \chem{\delta^{18}O} & ?\% & -5.6{\degree}C & \aref \\
    ODP~1012 & \chem{U^{K'}_{37}}  & ?\% & -5.8{\degree}C & \aref \\
    ODP~1020 & \chem{U^{K'}_{37}}  & ?\% & -5.8{\degree}C & \aref \\
    \bottomhline
  \end{tabular}}
  \belowtable{}
\end{table*}
